\documentclass[12pt, letterpaper]{article}
\usepackage[utf8]{inputenc}

\title{Entity}
\date{March 2022}

\begin{document}
The entity-relationship contains 8 main entities:
\begin{itemize}

\item Users: This is the entity where we collect information about all the people that work or come to the gym, they are identified from a Primary key (The fiscal code), and it’s necessary also to store all information in order to access their private pages . There are 3 types of users 
\begin{itemize}
	\item Trainer, if they held courses at the gym 
	\item Trainee for users which attend course
	\item Secretary: for workers that managed bureaucratics and sign presence
\end{itemize}
A single user may have more than one role,they are defined in the “Role” attribute. 

Password reset: This entity is necessary to manage the password reset system for our web app. When a user forgets his password we will send a token (via email address) which permits him to create a new password for his account. Tokens expire if they are not used after 30 minutes.
\item  Medical certificate: This entity is necessary to collect information about medical certificates. The medical certificate is mandatory for every user with a “trainee” role in order to attend the courses offered by the gym.
\item Course: Course is an entity to describe the different types of courses we have in our gym. We store the name and a description for our courses.
\item Course edition : it’s an entity that describes a course that is held by a trainer at specific times in our gym. Any occurence in this entity must match a course type from the “Course” entity
\item Lecture time slot
\item Subscription type
\item Subscription
\end{itemize}

\end{document}